Using best practices for forecasting biodiversity changes in breeding birds

### 2017-08-02 manuscript/draft.Rmd
Stuff

While the models generally did well in absolute terms (Figure 4), none
consistently outperformed the "average" baseline from the generalized linear
mixed model (Figure 4A). [[Stats go here]].  The auto-ARIMA was generally the
best-performing non-baseline model, but in many cases (67% of the time), the
auto.arima procedure automatically selected a model with no autoregressive,
drift, or moving average terms, making it similar to the "Average" model.

@@

Most models produced confidence intervals that were too narrow, indicating
overconfident predictions (Figure 4B). The random forest-based SDM stack was the
most overconfident model, with only `r numbers$rf_coverage_pct`% of observations
falling inside its 95% confidence intervals. This stacked SDM's narrow
predictive distribution also caused it to have notably higher deviance (Figure
4C) than the next-worst model, even though its point estimates were not
unusually bad in terms of RMSE (3A). As discussed elsewhere [@harris2015], this
overconfidence is a product of the assumption in stacked SDMs that errors in the
species-level predictions are independent. Because they avoided this assumption,
the GBM-based "macroecological" model and the mistnet JSDM had reasonably
well-calibrated uncertainty estimates (Figure 4B); as a result, their relative
performance was higher in terms of deviance than in terms of RMSE. The "naive"
model was the only model whose confidence intervals were too wide (Figure 4B),
which can be attributed to the rapid rate at which these intervals expand
(Figure 1).

>>>>

While the models generally did well in absolute terms (Figure 4), none
consistently outperformed the "average" baseline from the generalized linear
mixed model (Figure 4). The auto-ARIMA was generally the
best-performing non-baseline model, but in many cases (67% of the time), the
auto.arima procedure automatically selected a model with no autoregressive,
drift, or moving average terms, making it similar to the "Average" model.
All five alternatives to the "average" model achieved lower error on some
of the sites in some years, but each one had a higher mean absolute error
and higher mean deviance.

@@

Most models produced confidence intervals that were too narrow, indicating
overconfident predictions (Figure 5C). The random forest-based SDM stack was the
most overconfident model, with only `r numbers$rf_coverage_pct`% of observations
falling inside its 95% confidence intervals. This stacked SDM's narrow
predictive distribution also caused it to have notably higher deviance (Figure
5B) than the next-worst model, even though its point estimates were not
unusually bad in terms of RMSE (5A). As discussed elsewhere [@harris2015], this
overconfidence is a product of the assumption in stacked SDMs that errors in the
species-level predictions are independent. Because they avoided this assumption,
the GBM-based "macroecological" model and the mistnet JSDM had reasonably
well-calibrated uncertainty estimates (Figure 5B); as a result, their relative
performance was higher in terms of deviance than in terms of RMSE. The "naive"
model was the only model whose confidence intervals were too wide (Figure 5C),
which can be attributed to the rapid rate at which these intervals expand
(Figure 1).
